An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-09-17 poly-embed-journal/poly-embed-journal.tex
Pass on OP, top k, and Section 6 intro

@@

\subsection{Embedding Ordered Partitions}
\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.

An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
\begin{align*}
\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
\end{align*}
The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.

The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
\begin{equation}\label{eq:ww-hinge}
L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
\end{equation}

\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in S_i$, we have $\varphi(S)_j = -(i-1)$.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
	\caption{Level sets of $\psi \circ \prop{WW}$, the property elicited by Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.  
		$\prop{WW}$ is shown with faint dotted lines.}
	\label{fig:ordered-partition}
\end{figure}

\subsection{Inconsistency of top-$k$ losses}
In settings of search results and object recognition, one might plausibly be interested in top-$k$ classification: a generalization of $0-1$ loss where one can predict a set $S$ of size $k$, receiving loss $0$ if the true label $y \in S$, and $1$ otherwise.
While this problem is well-studied, \citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable} a class of surrogates for top-$k$, most of which are not simultaneously convex and consistent.
The only convex surrogate in the literature that is consistent is the softmax surrogate of~\citet{lapin2016loss} which essentially learns the entire distribution.
However, this seems to encapsulate more information than necessary and therefore presumably requires more data to learn the Bayes optimal hypothesis.
\jessie{Add more here}

Other hinge-like surrogates are shown to be non-consistent by~\citet{lapin2016loss} and~\citet{yang2018consistency}, including $\psi_2$ from~\citet[Table 1]{yang2018consistency}, which elicits essentially the same property $\prop{WW}$ shown in Figure~\ref{fig:ordered-partition} before the link is applied for certain values of $n$ and $k$.

@@

\citet{TOPKPAPER} presents an embedding (Eq.~\eqref{eq:topk-embedding}) for top-$k$ loss that looks unlike the commonly studied surrogates in the literature.
Moreover, the most common link $\psi^{\tt argmax}(u) := \argmax_{S \subseteq \Y : |S| = k} \sum_{i \in S} u_i$ is an $\epsilon$-thickening of the embedding with $\epsilon = $ and the norm $\|\cdot\|_x$.\jessie{TODO... if this is true.}

@@

\raf{Brief overview here}
\raf{Add somewhere: initially explored by~\citet{wang2020weston} under the name \emph{embedding cardinality}}

@@

\begin{lemma}\label{lem:polyhedral-pd-same}
	Let $f_1,\ldots,f_m:\reals^d\to\reals$ be polyhedral convex functions.
	The power diagram induced by $\sum_{i=1}^m p_i f_i$ is the same for all $p \in \inter(\simplex)$.
\end{lemma}
\begin{proof}
	For any convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
	Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.
	It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter(F')$ with constant derivative $d\in\reals^d$.
	Conversely, for any subgradient $d'$ of $g$, the set of points $\{x\in\reals^d : d'\in\partial g(x)\}$ is the projection of a face of $P$; we conclude that $F = \{(x,g(x))\in\reals^{d+1} : d\in\partial g(x)\}$ and $F' = \{x\in\reals^d : d\in\partial g(x)\}$.

>>>>

\citet{wang2020weston} first studies the notion of minimum representative sets under the name \emph{embedding cardinality}.

@@

\subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
While the hinge loss is the most common surrogate for binary support vector machines (SVMs), original extensions to $n$-class prediction involved a one-vs-all reduction to the binary problem and generating ${n \choose 2}$ hyperplanes via hinge loss.
Proposing a more efficient solution,~\citet*{weston1999support} give an alternate surrogate for multiclass SVM prediction, though originally its consistency with respect to 0-1 loss remained open.
Regardless,~\citet{dogan2016unified} advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.
The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
\begin{equation}\label{eq:ww-hinge}
L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
\end{equation}

\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss, and in turn, show inconsistency with respect to 0-1 loss.
An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples $T = \{T_1, \ldots, T_l\}$ with $\emptyset \subsetneq T_1 \subsetneq \ldots \subsetneq T_l = [n]$ for some $l \geq 2$.
The ordered partition target loss $\ell^{\OP}$ is defined by
%An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
%The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
\begin{align*}
\ell^\OP(T,y) &= |T_1| - 1 + \sum_{i=1}^{l-1} |T_{i+1}| \cdot \Ind{y \not \in T_i}~.~
\end{align*}
The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in T_i \setminus T_{i-1}$, we have $\varphi(T)_j = -(i-1)$.

\begin{figure}[H]
	\begin{minipage}{0.5\linewidth}
	\centering
	\includegraphics[width=0.9\linewidth]{tikz/ordered-partition}
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
	\caption{Level sets of $\psi \circ \prop{WW}$, the property elicited by Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.  
		$\prop{WW}$ is shown with faint dotted lines.}
	\label{fig:ordered-partition}
	\end{minipage}
\end{figure}

\subsection{Inconsistency of top-$k$ losses}
In settings of search results and object recognition, one might plausibly be interested in top-$k$ classification: a generalization of 0-1 loss where one can predict a set $S$ of size $k$, receiving loss $0$ if the true label $y \in S$, and $1$ otherwise.
While this problem is well-studied, \citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable} most surrogates for top-$k$ are not simultaneously convex and consistent.
Those that are essentially elicit the distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$~\citep{lapin2016loss}.
%The only convex surrogate in the literature that is consistent is the softmax surrogate of~\citet{lapin2016loss} which essentially learns the entire distribution.
However, this seems to encapsulate more information than necessary and therefore presumably requires more data to learn the Bayes optimal hypothesis than learning the less granular top-$k$ property.

Other hinge-like surrogates are shown to be non-consistent by~\citet{lapin2016loss} and~\citet{yang2018consistency}.
For example, $\psi_2$ from~\citet[Table 1]{yang2018consistency} elicits essentially the same property $\prop{WW}$ shown in Figure~\ref{fig:ordered-partition} before the link is applied for certain values of $n$ and $k$.
\citet{TOPKPAPER} applies the embedding framework to these surrogates to understand the target problems for which they are consistent.

@@

Moreover, \citet{TOPKPAPER} presents an embedding (Eq.~\eqref{eq:topk-embedding}) for top-$k$ loss that looks unlike the commonly studied surrogates in the literature.
Moreover, the most common link $\psi^{\tt argmax}(u) := \argmax_{S \subseteq \Y : |S| = k} \sum_{i \in S} u_i$ is calibrated for the surrogate in Equation~\eqref{eq:topk-embedding}.\jessie{TODO... confirm this is true.}
Their proof uses the $\epsilon$-thickened link construction from \S~\ref{sec:calibration} to understand which choices of linked values are feasible and align these choices with the argmax link.

@@

\jessie{Attempted brief overview}
In \S~\ref{sec:poly-loss-embed}, we discussed the connection between embeddings and polyhedral losses, and a natural next question is to understand if polyhedral losses are necessary to embed a discrete loss --- the answer is negative.
Here, we further study the structure of embeddings, showing instead that discrete losses must be embedded by a function with polyhedral Bayes risk, which have finite minimum representative sets.
For intuition, we show in \S~\ref{subsec:match-BR} that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
Since surrogates with polyhedral Bayes risk have finite minimum representative sets, we introduce and study the notion of a trimmed loss, and connect this to tight embeddings and non-redundancy from property elicitation.

\raf{Add somewhere: initially explored by~\citet{wang2020weston} under the name \emph{embedding cardinality} }
\jessie{Feels like we should mention that earlier, when minimum representative set is introduced? -- mentioned it right under the definition of representative set}

@@

\begin{lemma}\label{lem:polyhedral-pd-same}
	Let $f_1,\ldots,f_m:\reals^d\to\reals$ be polyhedral convex functions.
	The power diagram induced by $\sum_{i=1}^m p_i f_i$ is the same for all $p \in \inter(\simplex)$.
\end{lemma}
\begin{proof}
	For any polyhedral convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
	Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.
	It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter(F')$ with constant derivative $d\in\reals^d$.
	Conversely, for any subgradient $d'$ of $g$, the set of points $\{x\in\reals^d : d'\in\partial g(x)\}$ is the projection of a face of $P$; we conclude that $F = \{(x,g(x))\in\reals^{d+1} : d\in\partial g(x)\}$ and $F' = \{x\in\reals^d : d\in\partial g(x)\}$.
